### 2019-05-13 report/chapter03.Rnw
Changes after Discussion w Prof. Held

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8.1, fig.height=3.4,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

<<echo=FALSE>>= 
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

data = pb.readData(path = PATH_DATA, file = FILE)
tmp = pb.clean(data)
data = tmp[[1]]
aliases = tmp[[2]]

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else { 
  meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else { 
  meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

meta <- pb.meta.merge(meta.bin, meta.cont)

@@

require(biostatUZH)
require(tidyverse)
require(meta)
require(metasens)
require(gridExtra)
require(xtable)
@

@@

change.ranef.bin <- meta.bin %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% mutate(sig.change = factor(sig.change)) %>% group_by(sig.change, correction.method) %>% count()

p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
         label = paste(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n, "changed to nonsig."), 
         color = "white")

change.ranef.cont <- meta.cont %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()

p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
         label = paste(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n, "changed to nonsig."), 
         color = "white")

change.ranef <- meta %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()

p.ranef.change <- meta %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
         label = paste(change.ranef[change.ranef$sig.change == 3,]$n, "changed to nonsig."), 
         color = "white")

#Fixed effects meta-analysis significance
change.fixef.bin <- meta.bin %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
         label = paste(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n, "changed to nonsig."), 
         color = "white")

change.fixef.cont <- meta.cont %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
  annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
         label = paste(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n, "changed to nonsig."), 
         color = "white")

change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()

p.fixef.change <- meta %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
         label = paste(change.fixef[change.fixef$sig.change == 3,]$n, "changed to nonsig."), 
         color = "white")

# Significance after correction plots, separated for meta-analyses with significant publication bias test.
change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with significant small study effect")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>%   mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with non-significant small study effect")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

>>>>

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8.1, fig.height=3,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

<<echo=FALSE>>= 
rm(list = ls())
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

# data = pb.readData(path = PATH_DATA, file = FILE)
# tmp = pb.clean(data)
# data = tmp[[1]]
# aliases = tmp[[2]]

file.dat <- "data.RData"
if (file.exists(file.path(PATH_RESULTS, file.dat))) {
  load(file.path(PATH_RESULTS, file.dat))
} else {
  data = pb.readData(path = PATH_DATA, file = FILE)
  tmp = pb.clean(data)
  data = tmp[[1]]
  aliases = tmp[[2]]
  save(data, file =  file.path(PATH_RESULTS, file.dat))
}

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

file.meta <- "meta.RData"
if (file.exists(file.path(PATH_RESULTS, file.meta))) {
  load(file.path(PATH_RESULTS, file.meta))
} else {
  meta <- pb.meta.merge(meta.bin, meta.cont)
  save(meta, file =  file.path(PATH_RESULTS, file.meta))
}

@@

require(biostatUZH)
require(tidyverse)
require(meta)
require(metasens)
require(gridExtra)
@

@@

change.ranef.bin <- meta.bin %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
	mutate(n = n/sum(n))

p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
         label = paste(round(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
         color = "white")

change.ranef.cont <- meta.cont %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
	mutate(n = n/sum(n))

p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
         label = paste(round(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
         color = "white")

change.ranef <- meta %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
	mutate(n = n/sum(n))

p.ranef.change <- meta %>% ungroup() %>% 
  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
         label = paste(round(change.ranef[change.ranef$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
         color = "white")
# Significance after correction plots, separated for meta-analyses with significant publication bias test.
#Fixed effects meta-analysis significance
#Binary outcomes:
change.fixef.bin <- meta.bin %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
	mutate(n = n/sum(n))

p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
         label = paste(round(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
         color = "white")

#Continuous outcomes:
change.fixef.cont <- meta.cont %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% 
  mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
	mutate(n = n/sum(n))

p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
         label = paste(round(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
         color = "white")

#Overall:
change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
	mutate(n = n/sum(n))

p.fixef.change <- meta %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
         label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
         color = "white")

#Separated for meta-analyses with significant publication bias test.
change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
	mutate(n = n/sum(n))

p.change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 250, 
           label = paste(round(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
           color = "white")

change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>%  
	mutate(n = n/sum(n))

p.change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>% 
	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$correction.method, y = 1300, 
           label = paste(round(change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
           color = "white")
